---
title: "Mini-Project 2"
author: "Starry Zhou, Fiona Miller, Josephine Nyoike"
date: "March 24, 2017"
output: html_document
---

## goals
1 write a function to find the portion of the contribution to one candidate
2 apply the function to multiple candidates (possibly several candidates in one state)
3 make a bar graph to show their comparison
could be all elections from state
who won vs contribution totals

## Loading the data

```{r, message=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
load("individuals.rda")
library(tidyverse)
```

## Five verbs
use select to just get candidates from one state (MA?)

```{r}

MA_only <- candidates %>% filter(cand_office_state == "MA", cand_election_yr== "2012")

contr_small <- select(contributions, cmte_id, transaction_amt, cand_id)

indv_small <- select(individuals, cmte_id, transaction_amt)
```


## Joining tables

join the candidate table with contributions and individuals also maybe committees?

```{r}
joined <- 
  MA_only %>%
  left_join(contr_small,by="cand_id")
joined
```

## Visual

What type of graph?

## Blog

explaining the visaul and what found from data

## Grading Rubric

To get full credit for this Mini-Project, you must earn 10 points out of the following 12:

Baseline

+1 for an .Rmd that compiles without errors
+1 for including the code that wrangled the data
+1 for using at least two of the five basic verbs (i.e., select(), mutate(), etc.)
+1 for annotating your data wrangling pipeline (this can be in a few sentences in text surrounding the R code chunks, or some informative comments inside the R code chunks)
+1 unnecessary messages from R are hidden from being displayed in the HTML
Average

+1 for explaining in a single coherent sentence what we can learn from these data
+1 for writing a function rather than re-writing the same code multiple times
+1 for using at least one join (e.g. left_join(), inner_join(), etc.)
+1 blog post text provides context or background useful in interpreting the graphic
+1 for using GitHub for version control
Advanced

+1 for using the Issues tab on GitHub to plan your project
+1 WOW factor: awarded at the professors’ discretion for submissions that are exceptionally compelling