---
title: "Mini-Project 2"
author: "Starry Zhou, Fiona Miller, Josephine Nyoike"
date: "March 24, 2017"
output: html_document
---

We analysised the candidates' contributions by commitees in MA, 2012. We selected candidates with known, positive contributions, and wrote a function to find the proportion of the contribution of one certain candidate to the total contributions to all candidates in MA. We learned from these data the donations that each candidate running in Massachusetts recieved in comparison to other candidates running in MA.

Scott P Brown, a republican running for the senate, recieved the largest proportion of the donations of the candidates in MA, and Adam G Chaprales, a republican running for the house, recieved the smaller proportion of the donations of candidates in MA. The top 5 candidates who recieved the largest proportion of the donations in MA were Scott P Brown (Republican running for senate), Elizabeth Warren(Democrat running for senate), John F Tierney (Democrat running for house), Richard R Tisei (Republican running for house), and Mr. Richard E Neal (Democrat running for house). Adding a visualization helped us view the proportions of the contributions more clearly. We can easily tell whose contributions were the most and who had little to no money contributed towards their campaign. From the visualization as well, we see that democrats had more candidayes with money contributed towards their campaign, and no Libertarian candidate appears on the bar chart. This shows that their contributions were non-existent in the data that we used. 

```{r, message=FALSE}
##Load data and tidyverse
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
load("individuals.rda")
library(tidyverse)
```

```{r}
## Select the information for candidates in Massachusetts in the year of 2012: we selected some information about contributions inlcuding candidates, party affliation, and office, and some information about individuals, inlcuding candidates whose transaction amount is positive and their transaction amount
MA_only <- candidates %>% filter(cand_office_state == "MA", cand_election_yr== "2012") %>%
  select(cand_id, cand_name, cand_party_affiliation, cand_office)

contr_small <- contributions %>%
  select(cmte_id, transaction_amt, cand_id) %>%
  filter(transaction_amt >0)

indv_small <- individuals %>%
  select(cmte_id, transaction_amt) %>%
  filter(transaction_amt >0)
```

```{r}
## Show all candidates in MA with their contributions by committees
joined <- 
  MA_only %>%
  left_join(contr_small,by="cand_id")
head(joined)
```

```{r}
## Change table joined into j2, remove column cmte_id, then find total committee contributions to candidate (so that contributions is only one row)
j2 <- joined %>%
  select(-cmte_id) %>%
  group_by(cand_id) %>%
  summarise(total = sum(transaction_amt))
## Join j2 back to MA_only so that the cand_id and donations are matched to information about the candidates
final <- 
  MA_only %>%
  left_join(j2, by="cand_id")
final
```

```{r}
##find total contributions to all candidates in MA
all <- final %>%
  summarise(N = sum(total,na.rm=TRUE))
all
```

```{r}
##create function to find proportion of donations one candidate gets in contrast to the other candidates in the state
person_prop <- function(id) 
  final %>%
    filter(cand_id == id) %>%
    summarize(prop=(total/(23351994))*100)%>%
    select(prop)
```

```{r}
##run the function to find the donations to a certain candidate (Barney Frank) to test function
person_prop(id="H0MA04036")
```


```{r}
##run the function to find the donation to all candidates with known donations with lapply
can_w_contr <- c("H0MA04036", "H0MA04119", "H0MA04127", "H0MA05066", "H0MA10082", "H2MA00014", "H2MA01020", "H2MA04040", "H2MA04073", "H2MA04107", "H2MA06078", "H2MA09072", "H2MA09213", "H4MA03022", "H4MA05043", "H4MA06033", "H6MA07101", "H8MA02041", "H8MA05143", "H8MA08071", "S0MA00109", "S2MA00113", "S2MA00139", "S2MA00170")
lapply(can_w_contr, FUN = person_prop) %>%
  bind_rows()
```
```{r}
## create a data visualization to compare the contributions to candidates in diffferent parties, differentiated by colors 
no_na <- final %>%
  select(cand_name, total, cand_party_affiliation) %>%
  filter(total >0)
```
```{r}
p1 <- ggplot(no_na, aes(x = cand_name , 
                          y = total, fill = cand_party_affiliation)) + 
    geom_bar(stat= "identity") +
  scale_fill_manual(values = c("#0000FF", "#FFFF00", "#FF0000"),(guide = guide_legend(title = "Party")),labels = c("Democrat", "Libertarian", "Republican"))+
  xlab("Candidate Name")+
  ylab("Total Contributions")
p1 + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
